Neighborhoods and Felony Disenfranchisement: The Case of New York City

### 2020-03-31 markdown/part1/UAR_submission.Rmd
write

Ultimately, the analysis at hand cannot answer the causal mechanism for these depressive effects, or why the depressive effect is concentrated in Black neighborhoods. As @Walker2020 notes, "contextual measures of proximity do not accurately assess the relational aspect central to the concept of proximal contact" (p 123). Administrative data can only get us so far. Other research designs are necessary to investigate how neighbors understand the incarceration of their neighbors, how they react on voting day, and whether these effects are racially moderated. Much of the work being done by Hannah Walker and coauthors [-@Walker2014; -@Walker2017; -@Walker2020] does point to racial differences in political responses to proximal contact with systems of incarceration.

>>>>

Ultimately, the analysis at hand cannot answer the causal mechanism for these depressive effects, or why the depressive effect is concentrated in Black neighborhoods. As @Walker2020 notes, "contextual measures of proximity do not accurately assess the relational aspect central to the concept of proximal contact" (p 123). Administrative data can only get us so far. Other research designs are necessary to investigate how neighbors understand the incarceration of their neighbors, how they react on voting day, and whether these effects are racially moderated. Much of the work being done by Hannah Walker and coauthors [@Walker2014; @Walker2017; @Walker2020] does point to racial differences in political responses to proximal contact with systems of incarceration.
